Knowledge Representation for Service Robots: A Survey

### 2014-04-28 letter-to-editor.tex
Final version letter to editor

Those systems or frameworks have rapidly grown in number over the last few
years: Since Brachman's and Levesque's book~\cite{brachman2004knowledge} in 
2004, dozens of systems have emerged to fulfil the need for explicit, symbolic (and
sub-symbolic) \emph{representation} and \emph{reasoning} on knowledge in
cognitive architectures for robots.\todo{MT: why do we survey only nine if there are dozens?}

Because these systems have explored many different paths, from building upon purely
logic languages to proposing distributed, diffuse knowledge representation
schemes; because more and more research groups that are looking for increased
robot autonomy look into the implementation of their own framework for knowledge
representation; because, also, no previous survey of these tools has ever been
published to the best of our knowledge, we propose to write such a review of the
existing literature, starting with brief typology of main features to be found
in those systems, followed by a systematic review of the existing approaches.

@@

\begin{tabular}{p{2.8cm}p{8cm}p{1.5cm}}
\toprule
{\bf Project} & {\bf Authors (Institution)} & Main references \\
\midrule
ARMAR/Tapas &  Holzapfel, Waibel \par (KIT Karlsruhe) &  \cite{Holzapfel2008}\\
CAST Proxies &  Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) &  \cite{Jacobsson2008} \\
GOLOG & Levesque (Toronto Univ.) & \cite{levesque1997golog} \\
GSM &  Mavridis, Roy \par (MIT MediaLab) & \cite{Mavridis2006} \\
Ke Jia Project & Chen et al. \par (Univ. of Science and Technology of China) &  \cite{Chen2010} \\
{\sc KnowRob} &  Tenorth, Beetz \par (TU Munich) &   \cite{Tenorth2009a} \\
NKRL &  Zarri et al. \par (Paris Est Créteil Univ.) &  \cite{Sabri2011} \\
%OBOC & KRS & Mendoza & & & & & \cite{Mendoza2005} \\
ORO &  Lemaignan, Alami \par (LAAS-CNRS) &  \cite{Lemaignan2010} \\
OUR-K/OMRKF &  Lim, Suh et al. \par (Hanyang Univ.) &   \cite{Lim2011, Suh2007} \\
PEIS KR\&R &  Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) &  \cite{Daoutis2009} \\
% & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\ % -> affordances, but no implementation on a robot
% & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\ % -> mostly planning under uncertainty
% & & Hertzberg (Osnabrück Univ.) \\ % -> affordances, semantic mapping
% (based on {\sc KnowRob} & & (JSK) \\

@@

\closing{Yours Sincerly,}

\ps{Séverin Lemaignan is with the CHILI Lab, EPFL, Lausanne, Switzerland.\\ 
    Moritz Tenorth is with the Institute for Artificial Intelligence, Universität Bremen, Germany.}

>>>>

Those systems or frameworks have rapidly grown in number over the last few
years: Since Brachman's and Levesque's book~\cite{brachman2004knowledge} in 
2004, numerous systems have emerged to fulfil the need for explicit, symbolic (and
sub-symbolic) \emph{representation} and \emph{reasoning} on knowledge in
cognitive architectures for robots.

Because these systems have explored many different paths, from building upon purely
logic languages to proposing distributed, diffuse knowledge representation
schemes; because more and more research groups that are looking for increased
robot autonomy look into the implementation of their own framework for knowledge
representation; because, also, no previous survey of these tools has ever been
published to the best of our knowledge, we propose to write such a review of the
existing literature. We plan to start with a broad overview of the existing techniques,
followed by a refined typology of the features to be found in knowledge
representation and reasoning systems, eventually followed by an in-depth review
of ten of these systems.

@@

\begin{tabular}{p{2.8cm}p{8cm}p{1.5cm}}
\toprule
{\bf Project} & {\bf Authors (Institution)} & Main references \\
\midrule
ARMAR/Tapas &  Holzapfel, Waibel \par (KIT Karlsruhe) &  \cite{Holzapfel2008}\\
CAST Proxies &  Wyatt, Hawes, Jacobsson, Kruijff \par (Brimingham Univ., DFKI Saarbrücken) &  \cite{jacobsson2008crossmodal} \\
GOLOG & Levesque (Toronto Univ.) & \cite{levesque1997golog} \\
GSM &  Mavridis, Roy \par (MIT MediaLab) & \cite{Mavridis2006} \\
Ke Jia Project & Chen et al. \par (Univ. of Science and Technology of China) &  \cite{Chen2010} \\
{\sc KnowRob} &  Tenorth, Beetz \par (TU Munich) &   \cite{Tenorth2009a} \\
NKRL &  Zarri et al. \par (Paris Est Créteil Univ.) &  \cite{Sabri2011} \\
%OBOC & KRS & Mendoza & & & & & \cite{Mendoza2005} \\
ORO &  Lemaignan, Alami \par (LAAS-CNRS) &  \cite{Lemaignan2010} \\
OUR-K/OMRKF &  Lim, Suh et al. \par (Hanyang Univ.) &   \cite{Lim2011, Suh2007} \\
PEIS KR\&R &  Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) &  \cite{Daoutis2009} \\
% & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\ % -> affordances, but no implementation on a robot
% & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\ % -> mostly planning under uncertainty
% & & Hertzberg (Osnabrück Univ.) \\ % -> affordances, semantic mapping
% (based on {\sc KnowRob} & & (JSK) \\

@@

\closing{Yours Sincerely,}

\ps{Séverin Lemaignan ({\tt severin.lemaignan@epfl.ch}) is with the CHILI Lab, EPFL, Lausanne, Switzerland.\\ 
Moritz Tenorth ({\tt tenorth@cs.uni-bremen.de}) is with the Institute for Artificial Intelligence, Universität Bremen, Germany.}
